Figures and Tables

### 2021-01-15 paper/figures_tables.Rmd
updates

```{r}
# shape
exptail <- 1
thintail <- 0.2
fattail <- 2

@@

ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
                color = "black", linetype = "dashed", size = 1.2) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
                color = "black", linetype = "dotted", size = 1.2) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
                color = "black", linetype = "solid", size = 1.2) +
  ylab("") + xlab("") +
  theme_bw()

@@

## Figure 4. 
Seed dispersal kernels produced by the three models considered

@@

@@

```{r movementdensity, fig.width=6, fig.height=2}

load("paper/simple_exp_runs.RData")

library(ggplot2)
library(dplyr)

# Figure for movement rates at the three levels

rates <- data.frame(level = "null", movrate = null_moverate$movrate[1]) %>%
  bind_rows(., indiv_moverate %>%
              rename(level = Bird_ID)) %>%
  bind_rows(., fam_moverate %>%
              rename(level = fam_g)) %>%
  mutate(model = ifelse(level == "null", "Null",
                        ifelse(level %in% paste0("f", 1:7), "Family", "Individual")))

n <- 1000
dens_rates <- NULL
for(i in 1:length(rates$level)) {
  dens_exp <- rexp(n, rate = 1/rates$movrate[i])

  out <- data.frame(level = rates$level[i], model = rates$model[i], value = dens_exp)
  dens_rates <- rbind.data.frame(dens_rates, out)
}

dens_rates %>%
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) %>%
  ggplot(., aes(x = value, group = level, color = model)) +
  facet_wrap(~model) +
  geom_density() +
  scale_color_manual(values = c("red", "grey", "black"), guide = "none") +
  theme_bw() + labs(x = "Distance in meters per minute") +
  #coord_cartesian(xlim = c(100, 300), ylim = c(0, 0.0025))+
  NULL
```

```{r grt, fig.width=3, fig.height=2}

n <- 10000
grt_dens <- data.frame(seq = 1:n, dat = (rgamma(n, shape = 4, scale = 5) + 8))
grt_data <- data.frame(time = round(sample(grt_dens$dat, 5)), seq = 1:5)
tt <- max(grt_data$time)
ggplot(grt_dens, aes(x = dat)) +
  geom_density() + 
  geom_point(data = grt_data, aes(x = time, y = 0)) +
  theme_bw() + labs(x = "Time in minutes")

>>>>

```{r fig.width=3, fig.height=2.5}
# shape
exptail <- 1
thintail <- 0.2
fattail <- 2

@@

ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
                color = "black", linetype = "dashed", size = 0.8) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
                color = "black", linetype = "dotted", size = 0.8) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
                color = "black", linetype = "solid", size = 0.8) +
  ylab("") + xlab("") +
  theme_bw()

@@

```{r}
load("paper/dispersal_kernels.RData")

## Figure 4. 
Seed dispersal kernels produced by the three models considered with Weibull distribution overlaid

```{r fig.width=3}
bind_rows(null_dispersal %>% mutate(model = "Null"), 
          indiv_dispersal %>% mutate(model = "Individual"),
          fam_dispersal %>% mutate(model = "Family")) %>% 
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> dispersal_data

dispersal_data %>% 
  ggplot(., aes(x = dispersal, group = model)) +
  facet_wrap(~model, nrow = 3) +
  geom_histogram(aes(y = ..density..), binwidth = 50) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white")) +
  labs(y = "Density", x = "Seed dispersal (m)")

```{r}
null_dispersal %>% 
  ggplot(., aes(x = dispersal)) +
  geom_histogram(aes(y = ..density..), binwidth = 50) +
  stat_function(fun = dweibull, n = 100, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2]),
                linetype = "solid", size = 1) +
  theme_bw() +
  labs(y = "Density", "Seed dispersal (m)") +
  lims(y = c(0, 0.004), x = c(0, 1500))
```

@@

null_dispersion %>% 
  mutate(model = "Null") %>% 
  bind_rows(indiv_dispersion %>% 
              mutate(model = "Individual")) %>% 
  bind_rows(fam_dispersion %>% 
              mutate(model = "Family")) %>% 
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> all_disp_data

all_disp_data %>% 
  ggplot(., aes(y = mean_dispersal, group = model)) +
  #facet_wrap(~model, ncol = 3) +
  geom_boxplot() +
  theme_bw()  +
  labs(y = "Seed dispersal (m)") -> b

all_disp_data %>% 
  ggplot(., aes(y = seed_dispersion)) +
  facet_wrap(~model, ncol = 3) +
  geom_boxplot() +
  theme_bw() +
  theme(strip.background = element_blank(),
        strip.text = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "Dispersion (m)") -> c

#plot_grid(a,b, nrow = 2)

# Edit redundant labels
# Fix names for axes

@@
